Considering scale in multilayer animal social networks

### 2020-06-23 paper/manuscript.Rmd
conclusion p

Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology. We demonstrate the novel analyses in varying social, spatial,
and temporal scale within a multilayer framework. We show that (1) multilayer
social networks are scale-dependent, and (2) the use of multilayer networks is
useful for identifying habitat or season-specific social processes. Our analysis
of caribou multilayer networks incorporating high resolution GPS telemetry data
and spatial land cover data is grounded in the context of observed animal social
networks, as the scales we chose to explore, e.g., number of observations and
sociality across space and time, are ones that have also traditionally been done
in ethology.
<!-- TODO: round it out -->

>>>>

Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology. We demonstrate the novel analyses in varying social, spatial, and
temporal scale within a multilayer framework. We show that (1) multilayer social
networks are scale-dependent, and (2) the use of multilayer networks is useful
for identifying habitat or season-specific social processes. Our multilayer
network analysis of caribou sociality incorporating high resolution GPS
telemetry data and spatial land cover data is grounded in the context of
observed animal behaviour as the scales we chose to explore, e.g., number of
observations and sociality across space and time, are ones that have also
traditionally been done in ethology.
<!-- TODO: round it out -->
